\section{Cryptographic Primitives}\label{sec:cryptographic-primitives}

In the interests of cryptographic minimalism, Veil uses just two distinct cryptographic primitives:

\begin{itemize}
    \item Keccyak-128~\cite{daemen2020,bertoni2018} for confidentiality, authentication, and integrity.
    \item NIST P-256 for key agreement and authenticity~\cite{fips1864}.
\end{itemize}

\subsection{Keccyak-128}\label{subsec:keccyak}

Keccyak-128 is the adaptation of the Cyclist duplex construction from Xoodyak~\cite{daemen2020} to the
Keccak-\emph{p}[1600,12] permutation instead of Xoodoo (thus ``Keccyak'').

Cyclist is a permutation-based cryptographic duplex, a cryptographic primitive that provides symmetric-key
confidentiality, integrity, and authentication via a single object~\cite{daemen2020}.
Duplexes offer a way to replace complex, ad-hoc constructions combining encryption algorithms, cipher modes,
AEADs, MACs, and hash algorithms using a single primitive~\cite{daemen2020, bertoni2011duplex}.
Duplexes have security properties which reduce to the properties of the cryptographic sponge, which themselves reduce to
the strength of the underlying permutation~\cite{bertoni2008}.

The Keccak-\emph{p}[1600,12] permutation is the basis of the KangarooTwelve hash algorithm~\cite{bertoni2018} and allows
for much higher throughput in software than the Xoodoo permutation at the expense of requiring a larger state.
It has a 1600-bit width, like Keccak-\emph{f}[1600] (the basis of SHA-3), but with a reduced number of rounds for speed.
Xoodyak's Cyclist parameters of $R_\text{hash}=b-256$, $R_\text{kin}=b-32$, $R_\text{kout}=b-192$, and
$\ell_\text{ratchet}=16$ are adapted for the larger permutation width of $b=1600$.
The resulting construction targets a 128-bit security level and is $\sim$4x faster than SHA-256, $\sim$5x faster
than ChaCha20Poly1305, and $\sim$7.5x faster than AES-128-GCM in software.

Veil's security assumes that Cyclist's \textsc{Encrypt} operation is IND-CPA secure, its
\textsc{Squeeze} operation is sUF-CMA secure, and its
\textsc{Encrypt}/\textsc{Squeeze}-based authenticated encryption construction is IND-CCA2 secure.

\subsection{P-256}\label{subsec:p256}

NIST P-256 is an elliptic curve with a prime-order cyclic group, which eliminates co-factor concerns~\cite{fips1864}.
This allows for the use of a wide variety of cryptographic constructions built on group operations.
The development of complete formulas for Weierstrass curves by Renes et al\.~\cite{renes2016} allows for simple
constant-time implementations, and the exclusive use of SEC1-encoded compressed points combined with strict checks
for the additive identity (a\.k\.a\. ``infinity'') and coordinate modularity eliminate malleability and invalid curve
attacks.

Veil's security assumes that the Gap Discrete Logarithm and Gap Diffie-Hellman problems are hard relative to P-256.
